High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-11-26 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star. %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, 
Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.

>>>>

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.***  %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, 
Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.
